prod_prep_mergedata

### 2025-01-09 07-apendice.qmd
change income vars

```{r multilevel-full, echo=FALSE, results='asis'}
df_study1 <- 
  df_study_long_t7_comunas %>%
  select(idencuesta,ola,comuna, ponderador_long_total,just_educ, des_perc, merit_effort, merit_talent, education=educ,quintil1:sexo) %>% 
  na.omit() %>% 
  mutate(ola = as.factor(ola),
         ola_num = as.numeric(ola),
         ola_2=as.numeric(ola)^2,
         sexo=as.factor(sexo)
         )
# Hipotesis
h0 <- "ola"
h1 <- "ola_num+ola_2"
h2 <- "ola_num+ola_2+education+quintil1+ess+edad+sexo"
h3 <- "ola_num+ola_2+education+quintil1+ess+edad+sexo+pos_id"
h4 <- "ola_num+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc"
h5 <- "ola_num+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent"
h6 <- "ola_num+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort"

# A. Education distributive justice
educ.null <- lmer(formula(paste0("just_educ~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ0 <- lmer(formula(paste0("just_educ~",h0,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ1 <- lmer(formula(paste0("just_educ~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ2 <- lmer(formula(paste0("just_educ~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ4 <- lmer(formula(paste0("just_educ~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ5 <- lmer(formula(paste0("just_educ~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ6 <- lmer(formula(paste0("just_educ~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)

@@

omit <- "(education)|(ess)"
texreg::htmlreg(list(educ0, educ1, educ3, educ4, educ5, educ6),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05.", 
#                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave 2017",
                                      "Wave 2018",
                                      "Wave 2019",
                                      "Wave 2022",
                                      "wave 2023",
                                      "Wave",
                                      "Wave^2",
                                      "High School",
                                      "Technical",
                                      "Universitary",
                                      "Quintile 2",
                                      "Quintile 3",
                                      "Quintile 4",
                                      "Quintile 5",
                                      "Quintile (No information)",
                                      "Subjective Social Status",
                                      "Age 30-49",
                                      "Age 50-64",
                                      "Age 65 or more",
                                      "Gender (Ref. Male)",
                                      "Center",
                                      "Right",
                                      "Does not identify",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: Effort" ),
                groups = list("Wave (Ref.= Wave 2016)" = 2:6,
                              "Education (Ref.=Primary)"= 9:11,
                  "Household Income (Ref.= Quintile 1)" = 12:16,
                  "Age (Ref.= 18-29)" = 18:20,
                  "Pol. pos (Ref.= Left)" = 22:24
                  ),
                include.loglik = FALSE,
                include.aic = FALSE,
                custom.gof.names = c("BIC",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual"),
               caption = paste("(\\#tab:multilevel-full)","Multilevel model for the justification of economic inequality"),
               center = TRUE,
               caption.above = TRUE,
               scalebox = 0.60,
               float.pos = "!ht", 
               booktabs = FALSE, 
               use.packages = FALSE, 
               include.rs = FALSE, 
               include.rmse = FALSE,
               include.ci = FALSE)

>>>>

```{r echo=FALSE, results='asis'}
#| label: tbl-multilevel-full
#| tbl-cap: "Complete multilevel longitudinal models for the justification of inequality in education"

pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t7_comunas %>%
  select(idencuesta,ola,comuna, ponderador_long_total,just_educ, des_perc, merit_effort, merit_talent, education=educ,quintil1:sexo, covid_economia, covid_beneficios, inc_pcmed) %>% 
  na.omit() %>% 
  mutate(ola = as.factor(ola),
         ola_num = as.numeric(ola),
         ola_2=as.numeric(ola)^2,
         sexo=as.factor(sexo)
         )

df_study1 <- df_study1 %>%
  group_by(idencuesta) %>%             # Agrupar por el identificador del participante
  mutate(n_participaciones = n()) %>%  # Contar el número de filas (participaciones) por participante
  ungroup()
#sjmisc::frq(df_study1$n_participaciones)
df_study1 <- df_study1 %>% filter(n_participaciones>1)

#, percentile_wave, bot_mid_top_wave, inc_pcmed, ratioincome, incomegrp
df_study1$covid_beneficios<- car::recode(df_study1$covid_beneficios, c("1=2; 2=1"))

# Hipotesis
h0 <- "ola"
h1 <- "ola_num+ola_2"
h2 <- "ola_num+ola_2+education+inc_pcmed+ess+edad+sexo"
h3 <- "ola_num+ola_2+education+inc_pcmed+ess+edad+sexo+pos_id"
h4 <- "ola_num+ola_2+education+inc_pcmed+ess+edad+sexo+pos_id+covid_economia"
h5 <- "ola_num+ola_2+education+inc_pcmed+ess+edad+sexo+pos_id+covid_economia+covid_beneficios"
h6 <- "ola_num+ola_2+education+inc_pcmed+ess+edad+sexo+pos_id+covid_economia+covid_beneficios+des_perc"
h7 <- "ola_num+ola_2+education+inc_pcmed+ess+edad+sexo+pos_id+covid_economia+covid_beneficios+des_perc+merit_talent"
h8 <- "ola_num+ola_2+education+inc_pcmed+ess+edad+sexo+pos_id+covid_economia+covid_beneficios+des_perc+merit_talent+merit_effort"

# A. Education distributive justice
educ.null <- lmer(formula(paste0("just_educ~","1 + (1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ0 <- lmer(formula(paste0("just_educ~",h0,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ1 <- lmer(formula(paste0("just_educ~",h1,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ2 <- lmer(formula(paste0("just_educ~",h2,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ4 <- lmer(formula(paste0("just_educ~",h4,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ5 <- lmer(formula(paste0("just_educ~",h5,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ6 <- lmer(formula(paste0("just_educ~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ7 <- lmer(formula(paste0("just_educ~",h7,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ8 <- lmer(formula(paste0("just_educ~",h8,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)

@@

#omit <- "(edad)|(ess)|(sexo)|(pos_id)"
texreg::knitreg(list(educ0, educ1, educ3, educ4, educ5, educ6,educ7,educ8),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05.", 
 #               omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave 2017",
                                      "Wave 2018",
                                      "Wave 2019",
                                      "Wave 2022",
                                      "Wave 2023",
                                      "Wave",
                                      "Wave^2",
                                      "Universitary (Ref.= Less than universitary)",
                                      "Income",
                                      # "High School",
                                      # "Technical",
                                      # "Universitary",
                                      # "Quintile 2",
                                      # "Quintile 3",
                                      # "Quintile 4",
                                      # "Quintile 5",
                                      # "Quintile (No information)",
                                      "Subjective Social Status",
                                       "Age 30-49",
                                       "Age 50-64",
                                       "Age 65 or more",
                                       "Gender (Ref. Male)",
                                       "Center",
                                       "Right",
                                       "Does not identify",
                                      "Covid: economy more important than health",
                                      "Covid: receive state benefits",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: Effort"),
                groups = list("Wave (Ref.= Wave 2016)" = 2:6,
                          #    "Education (Ref.= Primary)" = 9:11,
                  #"Household Income (Ref.= Quintile 1)" = 12:16
                  "Age (Ref.= 18-29)" = 12:14,
                  "Pol. pos (Ref.= Left)" = 16:18
                  ),
                include.loglik = FALSE,
                include.aic = FALSE,
 #               custom.gof.rows = list("Controls"= c("No", "No", rep("Yes", 6))),
                custom.gof.names = c("BIC",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual"),
               center = TRUE,
               caption.above = TRUE,
               scalebox = 0.765,
               float.pos = "!ht", 
               booktabs = FALSE, 
               use.packages = FALSE, 
               include.rs = FALSE, 
               include.rmse = FALSE,
               include.ci = FALSE)

### 2025-01-09 production/prod_prep-mergedata.Rmd
change income vars

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo,
               esc_cit17) %>% 
 dplyr::rename(comuna=comuna.x)

@@

df_study2_long_comunas <- 
 dplyr::left_join(x = df_study2_long,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo,
               esc_cit17) %>% 
 dplyr::rename(comuna=comuna.x)

@@

df_study_long_t7_comunas <- 
 dplyr::left_join(x = df_study1_long_t7,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo,
               esc_cit17) %>% 
 dplyr::rename(comuna=comuna.x)

@@

df_study1_long_comunas$prom_simce_comuna_rescaled <- df_study1_long_comunas$prom_simce_comuna / 10
df_study1_long_comunas$var_simce_comuna_rescaled <- df_study1_long_comunas$var_simce_comuna / 100
df_study_long_t7_comunas$prom_simce_comuna_rescaled <- df_study_long_t7_comunas$prom_simce_comuna / 10
df_study_long_t7_comunas$var_simce_comuna_rescaled <- df_study_long_t7_comunas$var_simce_comuna / 100
# Verificar el rescalado
summary(df_study1_long_comunas$prom_simce_comuna_rescaled)
summary(df_study1_long_comunas$var_simce_comuna_rescaled)
# save data____________________________________________________________________
save(df_study1_long_comunas,
     file = here::here("input/data-proc/df_study1_long_comunas.RData"))
save(df_study2_long_comunas,
     file = here::here("input/data-proc/df_study2_long_comunas.RData"))
save(df_study_long_t7_comunas,
     file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))

>>>>

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo, percentile_wave, bot_mid_top_wave, inc_pcmed, ratioincome, incomegrp,
               esc_cit17) %>% 
 dplyr::rename(comuna=comuna.x)

@@

df_study2_long_comunas <- 
 dplyr::left_join(x = df_study2_long,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo, percentile_wave, bot_mid_top_wave, inc_pcmed, ratioincome, incomegrp, 
               esc_cit17) %>% 
 dplyr::rename(comuna=comuna.x)

@@

df_study_long_t7_comunas <- 
 dplyr::left_join(x = df_study1_long_t7,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo, percentile_wave, bot_mid_top_wave, inc_pcmed, ratioincome, incomegrp,
               esc_cit17) %>% 
 dplyr::rename(comuna=comuna.x)

@@

df_study1_long_comunas$prom_simce_comuna_rescaled <- df_study1_long_comunas$prom_simce_comuna / 10
df_study1_long_comunas$var_simce_comuna_rescaled <- df_study1_long_comunas$var_simce_comuna / 100
df_study_long_t7_comunas$prom_simce_comuna_rescaled <- df_study_long_t7_comunas$prom_simce_comuna / 10
df_study_long_t7_comunas$var_simce_comuna_rescaled <- df_study_long_t7_comunas$var_simce_comuna / 100
# Verificar el rescalado
summary(df_study1_long_comunas$prom_simce_comuna_rescaled)
summary(df_study1_long_comunas$var_simce_comuna_rescaled)
```

```{r}
# save data____________________________________________________________________
save(df_study1_long_comunas,
     file = here::here("input/data-proc/df_study1_long_comunas.RData"))
save(df_study2_long_comunas,
     file = here::here("input/data-proc/df_study2_long_comunas.RData"))
save(df_study_long_t7_comunas,
     file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
